%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Original author:
% Ayush K Singh
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring
% the document.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage{hyperref}
\usepackage[left=0.75in,top=0.6in,right=0.75in,bottom=0.6in]{geometry} % Document margins

\name{Ayush K Singh}
\address{(857)~302-9712 \\ 54 Burbank St. \\ Boston, MA}
\address{\href{github.com/singhay}{github.com/singhay} \\ \href{mailto:singhay@ccs.neu.edu}{singhay@ccs.neu.edu} \\ \href{linkedin.com/in/singhay}{linkedin.com/in/singhay}}

\begin{document}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection}{Northeastern University}{Boston, MA}{Master of Science in Computer Science}{Expected - Dec. 2017}
\item Coursework: Machine Learning, Distributed Systems \& Cloud Computing, PGM and Parsimonious Modeling, Algorithms, Cognitive Computing \& Deep Learning, Parallel Data Processing in MapReduce
\item Received \href{http://www.northeastern.edu/data-analytics/data-science-certificate/}{Graduate Certificate} in Data Analytics $i.e.$ Stats, Mining, Storing, Visualization.
\item Developed command line interface to \href{https://github.com/singhay/ms-courses-code/tree/master/CS5600-Computer-Systems/team-05-hw1-master}{simulate Unix shell} and \href{https://github.com/singhay/ms-courses-code/tree/master/CS5600-Computer-Systems/team-05-hw2-master}{file system} in C.
\item Built a \href{https://github.com/singhay/ms-courses-code/tree/master/CS7680-Cloud-Computing-Distributed-Systems}{VM to provision on premise resources} from AWS for scaling apps at peak workloads.
\item Developed a learning to rank \href{https://github.com/singhay/ms-courses-code/tree/master/CS6140-Machine-Learning}{game rating system} improving conventional rating system by 8\%.
\item Programmed solutions for \href{https://github.com/singhay/ms-courses-code/tree/master/CS5010-Programming-Design-Paradigm}{graph search, animations and inventory management} in Scheme.
\end{rSubsection}

\begin{rSubsection}{Graphic Era University}{Dehradun, India}{Bachelor of Technology in Computer Science \& Engineering}{Sept. 2010 - Aug. 2014}
\item Coursework: Software Engineering, Design \& Analysis of Algorithms, Computer Architecture, \\ Computer Networks, Operating System Concepts, Database Management Systems, OOP Concepts
\item Location based Online Grocery Store
\begin{rSubsubsection}
\item Developed a responsive single page app in MEAN storing sessions in Redis.
\item Devised tool to monitor inventory, track sales \& app performance using statsD - Graphite.
\item Built an item-item similarity based collaborative filtering recommender using Spark MLlib.
\end{rSubsubsection}
\item Developed Official College Festival \href{http://iblong2iyush.github.io/grafest}{website} using JavaScript, and Google Docs API.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{TripAdvisor}{Boston, MA}{Software Engineer Co-op}{May 2016 - Dec. 2016}
\item Improved personalization from time weighted to collaborative filtering getting 17\% sales hike.
\item Built an end to end admin app for support team to update subscriber’s details in MEAN Stack.
\item Developed log processor to categorize, process and visualize exim logs in python, Kafka, ELK.
\item Built personalized attractions and subject line recommender at hack days in R, python.
\item Automated the process of setting up workspace for bootstrapping new hires in bash.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Indian Defence Research and Development Organization}{Agra, India}{Intern}{July 2013 - Sep. 2013}
\item Converted entire paper oriented equipment demand system to online portal using LAMP stack reducing the processing time by 20\%.
\item Assisted scaling the application horizontally to functional departments of the Organization.

\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & C, C$++$, Python, JavaScript, Java, Scheme, \LaTeX \\
Big Data & R, Spark, Map Reduce, Spark, Hive, Pig, ELK, Kafka, Tableau \\
Databases & MySQL, RedShift, MongoDB, Elasticsearch, Solr, Redis, Cassandra \\
ML and AI & Theano, TensorFlow, Keras, scikit-learn, NumPy, pandas, seaborn, Caffe \\
Web & HTML, CSS, JSP, PHP, NodeJS, AngularJS, ReactJS, jQuery, Django, SpringMVC
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}
