%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% Original author:
% Ayush K Singh
%
% Important note:
% This template requires the resume.cls file to be in the same directory as the
% .tex file. The resume.cls file provides the resume style used for structuring
% the document.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass{resume} % Use the custom resume.cls style

\usepackage{multicol}
\usepackage{lipsum}% dummy text
\usepackage{hyperref}
\usepackage[left=0.75in,top=0.5in,right=0.75in,bottom=0.5in]{geometry} % Document margins

\name{Ayush K Singh}
\address{(857)~302-9712 \\ 54 Burbank St. \\ Boston, MA}
\address{\href{github.com/singhay}{github.com/singhay} \\ \href{mailto:singhay@ccs.neu.edu}{singhay@ccs.neu.edu} \\ \href{linkedin.com/in/singhay}{linkedin.com/in/singhay}}

\begin{document}

% \setlength{\columnseprule}{0.4pt}

% \begin{multicols}{3}

% (857)~302-9712 Ayush K Singh \href{github.com/singhay}{github.com/singhay} \\ 54 Burbank St. Boston, MA \\
%  Available: May - August \\
%  \href{mailto:singhay@ccs.neu.edu}{singhay@ccs.neu.edu} \\ \href{linkedin.com/in/singhay}{linkedin.com/in/singhay}

% \end{multicols}

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Summary}
Dedicated Web Developer and Big Data Analyst committed to the growth of Organization. With strong work ethics and professional demeanor, I bring excellent problem solving skills, technology agnostic quick learning attitude and resposible work ownership of diverse projects.
\end{rSection}

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

\begin{rSubsection}{Northeastern University}{Boston, MA}{Master of Science in Computer \& Data Science}{Sept. 2015 - Dec. 2017}
\item \textbf{Coursework} \href{http://www.ccs.neu.edu/home/vip/teach/MLcourse/html/}{Machine Learning}, \href{https://okrieg.github.io/EC500/index-spring-2016.html}{Distributed Systems \& Cloud Computing}, \href{http://www.ccs.neu.edu/home/eelhami/courses_nu_cs7180.htm}{High Dimensional Data Analysis}, Cognitive Computing \& Deep Learning, \href{http://www.ccs.neu.edu/home/mirek/classes/2012-F-CS6240/}{Parallel Data Processing in MapReduce \& Spark} \smallskip
% \item Developing a framework to compress redundant Neural Networks for Deep Learning on FPGA.
% \item Researching on parameter estimation and finding elimination ordering in bipartite clinical PGM.
\item Built model to predict bird sightings from mining \href{http://www.ccs.neu.edu/home/mirek/papers/ebird-ref-data.pdf}{eBird Dataset} using MapReduce with 82.6\% accuracy.
\item Deployed a Cloud Architecture \href{https://github.com/singhay/ms-courses-code/tree/master/CS7680-Cloud-Computing-Distributed-Systems}{to provision on premise resources} from AWS for scaling apps at peak workloads.
\item Developed a learning to rank \href{https://github.com/singhay/ms-courses-code/tree/master/CS6140-Machine-Learning}{player rating system} improving conventional rating system by 8\%.
\item Developed command line interface to \href{https://github.com/singhay/ms-courses-code/tree/master/CS5600-Computer-Systems/team-05-hw1-master}{simulate Unix shell} and \href{https://github.com/singhay/ms-courses-code/tree/master/CS5600-Computer-Systems/team-05-hw2-master}{file system} in User Space in C.
%\item Programmed solutions for \href{https://github.com/singhay/ms-courses-code/tree/master/CS5010-Programming-Design-Paradigm}{graph search, animations and inventory management} in Scheme.
\end{rSubsection}

\begin{rSubsection}{Graphic Era University}{Dehradun, India}{Bachelor of Technology in Computer Science \& Engineering}{Sept. 2010 - Aug. 2014}
\item \textbf{Coursework} Software Engineering, Design \& Analysis of Algorithms, Computer Architecture, \\ Computer Networks, Operating System Concepts, Database Management Systems, OOP Concepts \smallskip
\item Online Grocery Store
\begin{rSubsubsection}
\item Developed a responsive single page app in MySQL, AngularJS and NodeJS storing sessions in Redis.
\item Devised tool to monitor inventory, sales and app performance analytics using statsD, Grafana, d3JS.
\item Incorporated an item-item similarity based collaborative filtering recommender using Spark MLlib.
\end{rSubsubsection} \smallskip
\item Developed Official College Festival \href{http://iblong2iyhttps://preview.overleaf.com/public/qycvbyjhwrmh/images/78709a256178de9896998a942796c447cb008f76.jpegush.github.io/grafest}{website} using JavaScript, and Google Docs API.
\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Experience}

\begin{rSubsection}{TripAdvisor}{Boston, MA}{Software Engineer Co-op}{May 2016 - Dec. 2016}
\item Improved personalization from time weighted to collaborative filtering resulting in 17\% sales hike.
\item Built a web app for support team to update subscriber’s details in MySQL, AngularJS and NodeJS with autocomplete search engine, activity logs, LDAP authorization and extensive form handling routines.
\item Developed log processor to categorize, and process realtime exim logs in python from a  Kafka event stream, saving results in ElasticSearch and visualizing it in Kibana dashboards.
\item Created and added natural language processing Email Subject Line scoring model to CRM platform from in house dataset adding immediate boost in email open rates.
%\item Automated the process of setting up workspace for bootstrapping new hires in bash.
\end{rSubsection}

%------------------------------------------------

\begin{rSubsection}{Indian Defense Research and Development Organization}{Agra, India}{Intern}{July 2013 - Sep. 2013}
\item Built an web app using Linux Operating System, Apache Web Server, MySQL Database, and PHP stack cutting the manual application processing time from three months to two weeks.
\item Developed automated data report generation pipeline using macros in EXCEL \& CMD scripting and prepared dashboards to show descriptive statistics and analyze data key points.
%\item Assisted scaling the application horizontally to functional departments of the Organization.

\end{rSubsection}

\end{rSection}

%----------------------------------------------------------------------------------------
%	TECHNICAL STRENGTHS SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Skills}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Languages & C, Python, Java, JavaScript, Scala, R, Bash, PHP, \LaTeX \\
ML & TensorFlow, Keras, H2O, scikit-learn, Caffe, MXNet \\
Databases & MySQL, RedShift, MongoDB, Elasticsearch, Solr, Redis, HBase \\
Big Data & Spark, Map Reduce, Hive, Pig, ELK, Kafka, Tableau, AWS, OpenStack \\
Web & HTML, CSS, JSP, PHP, NodeJS, AngularJS, ReactJS, jQuery, Django, SpringMVC
\end{tabular}

\end{rSection}

%----------------------------------------------------------------------------------------

\end{document}